A general Nullstellensatz for generalized spaces

### 2019-04-05 slides-birmingham2019.tex
Explanations for some terms

@@

\setbeamertemplate{frametitle}{%
  \vskip1.2em%
  \leavevmode%
  \begin{beamercolorbox}[dp=1ex,center]{}%
  %   \usebeamercolor[fg]{item}{\textbf{{\Large \insertframetitle}}}
    \begin{tikzpicture}
      \def\R{8pt}
      \node (title) {\hil{\insertframetitle}};
      \begin{pgfonlayer}{background}
      \draw[decoration={bumps,segment length=8pt}, decorate, very thick, draw=mypurple]
        ($(title.south west) + (\R, 0)$) arc(270:180:\R) --
        ($(title.north west) + (0, -\R)$) arc(180:90:\R) --
        ($(title.north east) + (-\R, 0)$) arc(90:0:\R) --
        ($(title.south east) + (0, \R)$) arc(0:-90:\R) --
        cycle;
      \end{pgfonlayer}
    \end{tikzpicture}
  \end{beamercolorbox}%
}

@@

\newcommand{\mynav}[3]{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex]{}%
    \begin{columns}
      \begin{column}{0.333\textwidth}
        \raggedright
        \textcolor{#1}{\qquad\qquad Summary}
        \par
      \end{column}
      \begin{column}{0.333\textwidth}
        \centering
        \textcolor{#2}{The forcing model}
        \par
      \end{column}
      \begin{column}{0.333\textwidth}
        \raggedleft
        \textcolor{#3}{Revisiting the test cases \qquad\qquad}
        \par
      \end{column}
    \end{columns}
  \end{beamercolorbox}%
}

@@

  6th Workshop on Formal Topology in Birmingham \\
  April 11st, 2019
  \par

  \jnote{1}{We can associate to any reduced ring~$A$ a \emph{forcing
  model}~$A^\sim$.
  \begin{itemize}
    \item The forcing model has the pleasant property that it is a field.
    \item Reasoning about it requires that we restrict ourselves to
    intuitionistic logic.
  \end{itemize}
  Details are on the following slides.}
\end{frame}}

\begin{frame}{The mystery of nongeometric sequents}
  Let~$\TT$ be a geometric theory, for instance the theory of rings.

  % Illustration

  \textbf{Theorem.} There is a \hil{generic model}~$U_\TT$, a model such that
  for any geometric sequent~$\sigma$ the following notions coincide:
  \begin{enumerate}
    \item The sequent~$\sigma$ holds for~$U_\TT$.
    \item The sequent~$\sigma$ holds for any~$\TT$-model in any topos.
    \item The sequent~$\sigma$ is provable modulo~$\TT$.
  \end{enumerate}

  \justifying
  \textbf{Main observation.} The generic model can validate nongeometric
  sequents which are not provable modulo~$\TT$ and which do not hold for
  arbitrary models in arbitrary toposes.
\end{frame}

>>>>

\newcommand{\explain}[7]{%
  \tikz[remember picture,baseline]{
    \node[anchor=base,inner sep=2pt,outer sep=0,fill=#3,rounded corners] (label) {#1};
    \node[anchor=north,visible on=<#2>,overlay,rectangle callout,rounded corners,callout
    relative pointer={(0.0cm,0.5cm)+(0.0cm,#6)},fill=#3] at ($(label.south)+(0,-0.3cm)+(#4,#5)$) {#7};
  }%
}

@@

\setbeamertemplate{frametitle}{%
  \vskip0.6em%
  \leavevmode%
  \begin{beamercolorbox}[dp=1ex,center]{}%
  %   \usebeamercolor[fg]{item}{\textbf{{\Large \insertframetitle}}}
    \begin{tikzpicture}
      \def\R{8pt}
      \node (title) {\hil{\insertframetitle}};
      \begin{pgfonlayer}{background}
      \draw[decoration={bumps,segment length=8pt}, decorate, very thick, draw=mypurple]
        ($(title.south west) + (\R, 0)$) arc(270:180:\R) --
        ($(title.north west) + (0, -\R)$) arc(180:90:\R) --
        ($(title.north east) + (-\R, 0)$) arc(90:0:\R) --
        ($(title.south east) + (0, \R)$) arc(0:-90:\R) --
        cycle;
      \end{pgfonlayer}
    \end{tikzpicture}
  \end{beamercolorbox}%
  \vskip-0.6em%
}

@@

\newcommand{\mynav}[3]{%
  foo
}

@@

  6th Workshop on Formal Topology in Birmingham \\
  April 11st, 2019
  \par
\end{frame}}

\begin{frame}{The mystery of nongeometric sequents}
  Let~$\TT$ be a \explain{geometric theory}{4-}{red!20}{-1cm}{0cm}{0cm}{\begin{minipage}{4.3cm}
  sorts,
  function symbols,
  relation symbols,
  geometric sequents as axioms
  \end{minipage}}, for instance the
  \explain{theory of rings}{4-}{blue!20}{-1cm}{0cm}{0cm}{\begin{minipage}{4.3cm}
    \begin{tabbing}
      fun. symb.: \= \kill
      sorts: \> $R$ \\
      fun. symb.: \> $0$, $1$, $+$, $-$, $\cdot$ \\
      % rel. symb.: \> \emph{none} \\
      axioms: \> $(\top \vdash_{x,y:R} x y = y x)$, \ldots
    \end{tabbing}
  \end{minipage}}.

  % Illustration
  \vspace{2.5cm}

  \pause

  \textbf{Theorem.} There is a \hil{generic model}~$U_\TT$, a model such that
  for any \explain{geometric sequent}{4-}{yellow!70}{0cm}{0cm}{0cm}{
    a sequent of the form~$(\varphi \vdash_{x_1,\ldots,x_n} \psi)$
    where~$\varphi$ and~$\psi$ are geometric formulas
  }~$\sigma$ the following notions coincide:
  \begin{enumerate}
    \item The sequent~$\sigma$ holds for~$U_\TT$.
    \item The sequent~$\sigma$ holds for any~$\TT$-model in any
    \explain{topos}{4-}{purple!20}{0cm}{0cm}{0cm}{foo}.
    \item The sequent~$\sigma$ is provable modulo~$\TT$.
  \end{enumerate}

  \pause

  \justifying
  %\textbf{Main observation.} The generic model can validate nongeometric
  %sequents which are not provable modulo~$\TT$ and which do not hold for
  %arbitrary models in arbitrary toposes.

  \textbf{Observation (Kock).} The generic local ring is a field:
  \[ (x = 0 \Rightarrow \bot) \vdash_{x:R} (\exists y\?R\_ xy = 1) \]
\end{frame}
